Thread Pool in GeckoDB/BOLSTER - Implementing a Thread Pool for a high performance Database System \\

### 2018-06-23 Presentations/Paper/paper_thread_pool.tex
Add first version of related work to paper

\subsection{Experimental Configuration}
\textbf{TODO: Change?}\\The operating system is Ubuntu 17.04 with linux kernel version 4.13 running in a virtual machine on an Intel Core i7-6700HQ, 4x 2.6 GHz (Skylake) and 8GB DDR3 RAM running on 1600Mhz. We reduce the number of cores of the virtual machine to 4 instead of 8 virtual cores of the CPU. The CPU has 256KB L1 cache, 1MB L2 cache, and 6MB L3 cache. All simulations are repeated three times and a median value of all repetitions is used for evaluation.

@@

\section{Related Work}

\section{Conclusion and Future Work}

>>>>

\subsection{Experimental Configuration}
\textbf{TODO: Change!}\\The operating system is Ubuntu 17.04 with linux kernel version 4.13 running in a virtual machine on an Intel Core i7-6700HQ, 4x 2.6 GHz (Skylake) and 8GB DDR3 RAM running on 1600Mhz. We reduce the number of cores of the virtual machine to 4 instead of 8 virtual cores of the CPU. The CPU has 256KB L1 cache, 1MB L2 cache, and 6MB L3 cache. All simulations are repeated three times and a median value of all repetitions is used for evaluation.

@@

\section{Related Work}
Implementing multi threading can be realised using different approaches from spawning new threads to reuse them in thread pools. Pyarali et al. show that a thread pool model can significantly improve system performance and reduce response time \cite{pyarali2001evaluating}. They present different approaches to implement thread pools and show the dependency on use cases of these implementations.

Schmidt et al. present different implementations of multi threading, including two types of thread pools. They distinguish between the \emph{Worker Thread Pool Architecture} and the \emph{Leader/Follower Thread Pool Architecture} \cite{schmidt1998evaluating}. In the first approach, an IO-thread selects a connection, reads the requests and dispatches the tasks to an array of threads. Drawbacks of this system are excessive context switching effort along with synchronization required to manage the request queue. In the second approach, one thread of the pool becomes the leader and does the reading of the task into an internal buffer. If the request is valid, the thread itself processes the task and a follower thread becomes the new leader. This approach minimizes the context switching effort compared to the first one.

Along with the design of thread pool systems, the performance strongly depends on the number of threads used in a thread pool. Xu et al. present a performance study for a set of performance metrics combined with a heuristic algorithm for dynamic resizing of thread pools \cite{xu2004performance}. They show the correlation between average task idle time and the throughput of thread pools and present the effectiveness of dynamically adjusting the number of threads.

Compared to heuristically adjust the number of threads, Ling et al. formalized the problem of finding the optimal number of threads by establishing mathematical relationship among optimal thread pool size, system load and the associated costs \cite{ling2000analysis}. They show the applicability of their model and plan to further examine it based on additional metrics.
\section{Conclusion and Future Work}
